\Large \bf Conjure: Summoning Proxies from Unused Address Space

### 2019-05-15 paper/figures.tex
adding entropy figures.

\newcommand{\FigIpBits}{
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth,clip]{figures/ip-bits-set-pdf.pdf}
    \caption{\textbf{IPv6 Entropy}---%
        We observed 30 minutes of IPv6 traffic on our tap to the /32 of the ISP's network.
        In each address observed, we counted the number of bits set, and compared this to
        randomly generated addresses. If the 96 non-network bits
        of each address were chosen randomly, we would expect to see a Binomial distribution
        (shown as Random). In practice, the distribution of observed IP addresses has much fewer
        bits set, suggesting that censors might be able to distinguish between phantom host addresses
        and legitimate ones.\looseness=-1
        %We note there are several /64 subnets that had many
        %addresses that appeared random (visibly overlapping the random distribution).
    }
    \label{fig:ipbits}
\end{figure}
}

>>>>

\newcommand{\FigIpBits}{
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth,clip]{figures/ip-bits-set-pdf.pdf}
    \includegraphics[width=\linewidth,clip]{figures/entropy_curveball_1hr.png}
    \caption{\textbf{IPv6 Entropy}---%
        \textit{(Top)} In 30 minutes of IPv6 traffic observed on a /32 tap in 
        the ISP's network we counted the number of bits set in each address, and compared this to
        addresses generated from a uniform distribution. If the 96 non-network bits
        of each address were chosen randomly, we would expect to see a Binomial distribution
        (shown as Random). In practice, the distribution of observed IP addresses has much fewer
        bits set. \textit{(Bottom)} To further investigate this we captured one hour of IPv6 
        traffic at the same network tap and evaluated the entropy and aggregate count ratio 
        (ACR) across each nybble for the set of IPv6 addresses observed~\cite{foremski2016entropy}.
        The low entropy and high ACR in the upper nybbles can be attributed to the commonality 
        of the addresses associated with the specific /32 on which we captured. Overall the
        moderate entropy in most positions suggests that there is a relative structure to the way 
        IPv6 addresses are used but no rigid positions that would betray an individual IPv6 address. 
        Furthermore we can take consideration of that relative entropy when generating phantom 
        addresses.\looseness=-1
        % suggesting that censors might be able to distinguish between phantom host addresses
        % and legitimate ones.
        %We note there are several /64 subnets that had many
        %addresses that appeared random (visibly overlapping the random distribution).
    }
    \label{fig:ipbits}
\end{figure}
}

### 2019-05-15 paper/paper.tex
adding entropy figures.

\paragraph{Address entropy}
Addresses in IPv6 are commonly shortened, as many of the 128-bits in the address are set to 0.
For instance, google.com has the address
%\texttt{2607:f8b0:400f:0806:0000:0000:0000:2004} (which can be shortened to
\texttt{2607:f8b0:400f:806::2004}. Only 24~bits are set to 1 in this address,
giving censors a possible feature to filter on: addresses that have too much
entropy (or even simply bits set) could be suspicious as phantom hosts. To demonstrate and quantify
this problem, we measured 30 minutes of IPv6 traffic to our ISP's /32 network prefix.
Figure~\ref{fig:ipbits} shows a histogram of bits set in the addresses we observed, which are
notably skewed to less than expected if addresses were randomly generated. However, there
are still a significant number of networks that appear to have random-looking addresses,
making it difficult for censors to block these addresses outright. For a specific deployment,
operators should be careful to observe the distribution of addresses in the subnets they use,
and possibly limit to randomizing ``realistic'' bits (e.g. the middle and/or last 32 bits).

>>>>

\paragraph{Address entropy}
Addresses in IPv6 are commonly shortened, as many of the 128-bits in the address are set to 0.
For instance, google.com has the address
%\texttt{2607:f8b0:400f:0806:0000:0000:0000:2004} (which can be shortened to
\texttt{2607:f8b0:400f:806::2004}. Only 24~bits are set to 1 in this address,
giving censors a possible feature to filter on: addresses that have too much
entropy (or even simply bits set) could be suspicious as phantom hosts. To demonstrate and quantify
this problem, we measured 30 minutes of IPv6 traffic to our ISP's /32 network prefix.
Figure~\ref{fig:ipbits} shows a histogram of bits set in the addresses we observed, which are
notably skewed to less than expected if addresses were randomly generated. However, there
are still a significant number of networks that appear to have random-looking addresses,
making it difficult for censors to block these addresses outright.

Using one hour of collected traffic from the same tap we evaluated the entropy seen at
each nybble in a set of IPv6 addresses~\cite{foremski2016entropy}. The entropy and aggregate 
count ratio (ACR) for each position are used to group adjacent nybbles into probabilistically
related segments. We can see that all segments display at least moderate entropy 
suggesting that there is a structure to be mirrored in the way that IPv6 addresses are 
assigned. However, we note that in the dataset that we collected there is no position 
(outside of the upper bits related to the specific /32) that exhibited such low entropy
so as to be a signal to a censor on their own when evaluating a single suspect IPv6 address.

For a specific deployment, operators should be careful to observe the distribution of
addresses in the subnets they use, and possibly limit to randomizing ``realistic'' 
bits (e.g. the upper and/or last 32 bits within the given /32).
